|

### 2021-10-20 01-Chp-Background.Rmd
End of day:

Several statin treatments have been widely available for some time (see Table \@ref(tab:statinOverview-table)). Depending on the statin and dosage prescribed, the average reduction in LDL-c concentrations ranges from 15% with low-intensity regimen (e.g. ravastatin 5 mg/day) up to 60% with a high-intensity regimen (e.g. rosuvastatin 80 mg/day).[@collins2016a; @law2003] Statins also vary with regard to their lipophilicity (the extent to which they are lipid soluble), affecting their localisation within the body, with hydophilic statins being concentrated in the liver and lipophilic statins circualting more widely.[@schachter2005] This may create a divide in the pleiotropic affects of statins with differing lipophilicity, particularly given the ability of lipophilic statins to permeate the blood brain barrier.[@sierra2011]

>>>>

Several statin treatments have been widely available for some time (see Table \@ref(tab:statinOverview-table)). Depending on the statin and dosage prescribed, the average reduction in LDL-c concentrations ranges from 15% with low-intensity regimen (e.g. ravastatin 5 mg/day) up to 60% with a high-intensity regimen (e.g. rosuvastatin 80 mg/day).[@collins2016a; @law2003] Statins also vary with regard to their lipophilicity (the extent to which they are lipid soluble), affecting their localisation within the body, with hydophilic statins being concentrated in the liver and lipophilic statins circulating more widely.[@schachter2005] This may create a divide in the pleiotropic affects of statins with differing lipophilicity, particularly given the ability of lipophilic statins to permeate the blood brain barrier.[@sierra2011]
